Ethical considerations for computational implementation of health economic models

### 2024-02-15 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
for coauthor feedback draft

---
title: "MS_Aims"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---

In this paper, we <!--  MOVED_EDITED_START -->consider literature on modelling practice and draw on our prior experience with developing and using CHEMs to propose<!--  MOVED_EDITED_START -->:  (i) a set of ethical responsibilities for CHEM project teams<!-- and criteria for assessing ethical CHEM implementations -->;<!--  MOVED_EDITED_START --> (ii) attributes of CHEMs that can suggest fulfillment of these responsibilities; and (iii) criteria against which these attributes can be assessed.  <!--  MOVED_EDITED_END -->  
<!-- (i) some core ethical responsibilities of CHEM project teams;

>>>>

---
title: "MS_Aims"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
 <!-- Important rewordings --> 
In this paper, we <!--  MOVED_EDITED_START -->draw on our prior experience with developing and using CHEMs and consider literature on modelling practice to propose<!--  MOVED_EDITED_END -->:  (i) a set of ethical <!--  EDITED_Start responsibilities-->goals<!--  _EDITED_END --> for CHEM <!--  EDIT -->developers and funders<!--  /EDIT --<!-- and criteria for assessing ethical CHEM implementations -->;<!--  MOVED_EDITED_START --> (ii) attributes of CHEMs that suggest achievement of these goals; and (iii) criteria against which these attributes can be assessed.  <!--  MOVED_EDITED_END -->  
<!-- (i) some core ethical responsibilities of CHEM project teams;

### 2024-02-15 Markdown/Manuscript/Child_RMDs/MS_Conclusion.Rmd
for coauthor feedback draft

---
title: "MS_Conclusion"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
`r ifelse(is.na(params$X@conclusion_1L_chr),"",params$X@conclusion_1L_chr)` 
We have identified criteria that can be used to systematically assess the extent to which the computational implementation of health economic models adheres to transparency, reusability and updatability criteria. <!-- We have developed a prototype software framework that can support the implementation of CHEMs that largely meet these criteria. Our framework can be used as a prototype for developing future software frameworks to support ethical implementation of CHEMs.  --> Barriers to ethical CHEM practice arising from resource constraints should be addressed by research funders.

>>>>

---
title: "MS_Conclusion"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
`r ifelse(is.na(params$X@conclusion_1L_chr),"",params$X@conclusion_1L_chr)` 
<!-- We have identified criteria that can be used to systematically assess the extent to which the computational implementation of health economic models adheres to transparency, reusability and updatability criteria. <!-- We have developed a prototype software framework that can support the implementation of CHEMs that largely meet these criteria. Our framework can be used as a prototype for developing future software frameworks to support ethical implementation of CHEMs.  --> 
<!-- Barriers to ethical CHEM practice arising from resource constraints should be addressed by research funders. -->

### 2024-02-15 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
for coauthor feedback draft

Ethical practice is a core expectation of health researchers and computational methods underpin most quantitative research, yet an understanding of what constitutes ethical public health modelling practice is underdeveloped [@10.3389/fpubh.2017.00068]. We have addressed this gap with our proposed goals for model developers and funders, enabling CHEM attributes and CHEM implementation assessment criteria.

Currently, many if not most existing CHEMs are insufficiently transparent [@Jalali2021; @McManus2019; @Bermejo2017; @Ghabri2019], not reusable [@Feenstra2022; @Emerson2019], nor updatable [@Sampson2017; @10.3389/fpubh.2022.899874]. Addressing these issues will require changes to the tools, practices and funding underpinning health economic model development.

@@

<!-- Our software framework provides the outline of a technical solution to some of the challenges of open source CHEM development. However, better tools alone are insufficient and policy and institutional changes are also required.  -->
Reducing waste in research is a core responsibility of research funders [@chalmers2014increase] and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful. Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work and funding is rarely adequate to maintain and routinely update a model. Currently, it can take “an extraordinary amount of idealism” to commit to authoring and maintaining research software [@anzt2020environment]. Previously recommended strategies for more beneficial health economic research investments include support for harmonised ethical standards for model development [@10.3389/fpubh.2017.00068], methodological innovation to improve model transferability [@craig2018taking], networks of modellers working on common health conditions [@Sampson2019], and  centralized infrastructure such as open source model repositories [@Pouwels2022] and a standard platform for model implementations [@Ghabri2019].

<!-- Development of software frameworks to support ethical CHEM implementations could enable and enhance each of these strategies. --> ????

>>>>

Ethical practice is a core expectation of health researchers and computational methods underpin most quantitative research. However, an understanding of the ethical dimensions about how health economic models are implemented as software is underdeveloped. We have attempted to address this gap by proposing that CHEM developers and funders adopt the ethical goals of socially acceptable user requirements and design specifications, fit for purpose implementations and socially beneficial post-release use. We suggest that CHEM attributes of transparency, reusability and updatability are indicative of projects that meet these goals and have identified six criteria for assessing these attributes.

Prior literature has noted that health economic models routinely have limitations in transparency [@Jalali2021; @McManus2019; @Bermejo2017; @Ghabri2019], reuse [@Feenstra2022; @Emerson2019], and being kept up to date [@Sampson2017; @10.3389/fpubh.2022.899874]. These limitations not only pose ethical risks such as those we have described, but are practical barriers to model generalisability and transferability. Addressing these limitations will require changes to the work practices, funding and tools that underpin health economic model development.

Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020] and there is a need for better and comprehensive guidelines about how health economists should implement health economic models as software. Research funders need to actively support initiatives to help remove barriers to better practice in this area. A core responsibility of research funders is reducing waste in research [@chalmers2014increase]. Investments in modelling projects might generate greater social returns if they supported the project activities necessary to develop CHEMs that are easily understood, widely reused and well maintained.

Previously recommended strategies for more beneficial health economic research investments include support for harmonised ethical standards for model development [@10.3389/fpubh.2017.00068], methodological innovation to improve model transferability [@craig2018taking], networks of modellers working on common health conditions [@Sampson2019], and  centralized infrastructure such as open source model repositories [@Pouwels2022] and a standard platform for model implementations [@Ghabri2019]. Each of these strategies could benefit from enabling technical infrastructure, for example software frameworks that support the development of CHEMs that meet ethical criteria. We are currently engaged in developing a prototype of one such software framework [@ready4fw2024].

<!-- Development of software frameworks to support ethical CHEM implementations could enable and enhance each of these strategies. -->

@@

<!-- Our software framework provides the outline of a technical solution to some of the challenges of open source CHEM development. However, better tools alone are insufficient and policy and institutional changes are also required.  -->

### 2024-02-15 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
for coauthor feedback draft

To identify ethical issues that are specific to CHEMs, we <!-- first  -->considered <!-- Edit -->how Boden and McKendrick's four criteria might apply to <!-- /Edit -->the distinct phases in a software development project. Software development lifecycle (SDLC) models take different approaches to the inclusion, naming, definition, sequencing and iteration of project phases [@ruparelia2010software]. However, SDLC models typically have components that can principally map to the concepts of *planning* (e.g., identification of system / user requirements and design specifications), *implementation* (e.g., development and testing) and *release* (e.g., deployment, system integration, maintenance and support). For simplicity, we propose one overarching ethical <!-- responsibility  for CHEM project team-->goal for each phase. These goals<!-- responsibilities  --> are: 
<!-- establish  -->
(i) *socially acceptable user requirements and design specifications* (during CHEM planning);
<!-- ensure  -->
(ii) *fitness for purpose* (of CHEM implementations); and
<!-- support  -->
(iii) *socially beneficial use* (of CHEM releases).

Boden and McKendrick’s transparency criterion underpins the ethical goals we propose for all three phases (Table \@ref(tab:timelygls)). Boden and McKendrick’s other <!-- ethical  -->criteria can be selectively mapped to goals for specific phases: our proposed goal for ethical CHEM planning incorporates justice and independence considerations; the goal proposed for CHEM implementation is based on independence and beneficence / non-maleficence criteria; and the goal for ethical CHEM releases reflects beneficence / non-maleficence and justice criteria. <!-- /Edit -->

Misalignment between the values of computational model developers and those of the population groups affected by decisions based on their models presents significant ethical risks [@thompson2022escape; @duckett2022journey].  The value judgments of health economic modellers are rarely adequately specified [@duckett2022journey]. These value judgments influence the assumptions, selection of model features and standards for evidence that shape health economic model projects [@HARVARD2020112975]. For example, the process of determining CHEM *user requirements and design specifications* will involve making judgments about the competing claims of alternative software development platforms (Table \@ref(tab:timelygls)). That decision will in turn determine how straightforward it is for a CHEM to be subsequently amended to reflect alternative value judgments relating to model conceptualisation and mathematical formalisation (Table \@ref(tab:timelygls)).
<!-- Moved -->
<!--  , omissions that may lead to socially unacceptable policy recommendations -->

@@

The *social benefit* of developing a CHEM may be limited if it is rarely used, if mis-used or when its acceptability and adequacy rapidly decay. Reuse of CHEMs as components of other models can potentially make model development more efficient [@Arnold2010; @garcia2021cost]. However, health economic models face challenges related to transferability across jurisdictions [@garcia2021cost] that create barriers to reuse. Without ongoing maintenance, a CHEM risks becoming less reliable with time [@garcia2021cost] and is at risk of being deployed for purposes for which it is poorly suited [@calder2018computational]. Currently, health economic models are rarely implemented computationally in a manner that facilitates routine updates [@Sampson2017], thus limiting the temporal window within which a CHEM can be validly applied. 
<!-- Moved -->
<!-- Edit --><!-- All three  -->Our proposed ethical <!-- responsibilities  --> goals are most likely to be realised when there is both good<!-- have implications for both  -->professional practice by CHEM developers and <!-- Addition -->adequate <!-- Addition -->resourcing by project funders.  <!-- /Edit --> The choices CHEM developers make often need to balance ethical considerations with project resource constraints (as illustrated in Table \@ref(tab:proscons)). Modelling projects implemented by diligent and conscientious CHEM developers may still be exposed to ethical risks if there are inadequate resources to meaningfully engage relevant stakeholders, prepare code and data artefacts for independent assessment and provide ongoing model maintenance and user support. For these reasons, we believe responsibility for achieving our proposed ethical goals is shared between CHEM developers and funders. Reflecting the shared nature of this responsibility, we suggest that in most cases where a modelling project fails to meet our ethical goals, it will be more appropriate to describe these shortcomings as "ethical risks" (the language used by Boden and McKendrick) than to use accusatory terms like "unethical practice."<!-- these responsibilities should apply jointly to health economic model developers and funders. -->
<!-- For example, as illustrated in Table \@ref(tab:proscons), project resource constraints may require model developers to make trade-offs -->
<!-- As it is unreasonable to place expectations of modellers that they are not resourced to fulfil,  -->
<!-- /Moved -->

<!-- # -->
# CHEM attributes that can reduce ethical risk
<!-- The responsibilities of model project teams over a CHEM lifecycle  -->
Our proposed ethical goals for each project phase are are easier to state than to measure.  However, <!-- aspects of ethical modelling practice  -->achievement of these goals may be inferred from measurable attributes of CHEMs. As described in Table \@ref(tab:timelygls),  we believe that the <!-- Edit -->developers and funders<!-- /Edit --> of CHEMs that are transparent, reusable and updatable (TRU) are more likely to have achieved the ethical goals we propose. <!-- fulfilled a number of their ethical obligations.   --> 
<!-- We therefore selected these CHEM attributes to use as the basis for deriving ethical assessment criteria. -->

@@

Taking steps to make computational models *transparent* is an important means of reducing ethical risk<!-- part of ethical public health modelling practice  -->[@10.3389/fpubh.2017.00068]. Guidance on transparency in health economic modelling recommend that model code and data should be clearly documented [@Eddy2012]. Notably, the same guidelines, published over ten years ago, do not recommend sharing model code and data. However, more recent healthcare modelling guidance does recommend public dissemination of such artefacts [@Erdemir2020]. Online repository services such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection. Ensuring that calculations are correct and consistent with model specifications is an essential part of CHEM quality assurance [@techver2019]. The extensiveness of such verification checks can be reported using the concept of code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested. Tests should ideally combine both unit tests (to verify that small, isolated sections of code produce the correct output when run independently) and acceptance tests (to verify that the correct output is produced when multiple code components are run together to perform tasks that meet core user-requirements [@martin2003agile]). The nature and extent of individual model authorship contributions can become unclear when models are implemented over longer time-frames with a large and changing group of collaborators [@thompson2022escape]. This issue can be addressed by use of online repository services such as GitHub [@github2007], that provide citation tools and can transparently record all individual code contributions to a modelling project over its lifecycle.

<!-- A CHEM that is *reusable* also signals ethical modelling practice.  -->
Although making a CHEM’s code, data and documentation publicly available is increasingly considered good practice, it is insufficient to ensure that a model is *reusable*.  Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39]. Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is good scientific computing practice [@Wilson_2017] and promotes selective reuse. Computational implementations that store model code and data in distinct files and locations (as opposed to embedding data such as parameter values into source code) are also easier to selectively modify. Modular implementations enable models to be constructed from multiple independently reusable and replaceable sub-models (modules) [@pan2021modular]. The programming concept inheritance [@8717448], deployed in object-oriented programming approaches, can facilitate the duplication and selective modification of models. Granting permissions to others to use, test and adapt models and their components, can be facilitated by two broad categories of open source licenses. Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which content can be re-used. Alternatively, copyleft licenses [@copyleft2022] can be used to require that derivative works created by content users remain open-source.

@@

<!-- # -->
#	Criteria for assessing ethical computational implementations
For each CHEM attribute that suggests ethical CHEM modelling practice, we identified assessment criteria.

>>>>

To identify ethical issues that are specific to CHEMs, we <!-- first  -->considered <!-- Edit -->how Boden and McKendrick's four criteria might apply to <!-- /Edit -->the distinct phases in a software development project. Software development lifecycle (SDLC) models take different approaches to the inclusion, naming, definition, sequencing and iteration of project phases [@ruparelia2010software]. However, SDLC models typically have components that can principally map to the concepts of *planning* (e.g., identification of system / user requirements and design specifications), *implementation* (e.g., development and testing) and *release* (e.g., deployment, system integration, maintenance and support). For simplicity, we propose one overarching ethical <!-- responsibility  for CHEM project team-->goal for each phase. These goals<!-- responsibilities  --> are: 
<!-- establish  -->
(i) *socially acceptable user requirements and design specifications* (during CHEM planning);
<!-- ensure  -->
(ii) *fitness for purpose* (of CHEM implementations); and
<!-- support  -->
(iii) *socially beneficial use* (post CHEM release).

Boden and McKendrick’s transparency criterion underpins the ethical goals we propose for all three phases (Table \@ref(tab:timelygls)). Boden and McKendrick’s other <!-- ethical  -->criteria can be selectively mapped to specific phases: our proposed goal for ethical CHEM planning incorporates justice and independence considerations; the goal we propose for CHEM implementation is based on independence and beneficence / non-maleficence criteria; and our proposed ethical goal post CHEM release reflects beneficence / non-maleficence and justice criteria. <!-- /Edit -->

Misalignment between the values of computational model developers and those of the population groups affected by decisions based on their models presents significant ethical risks [@thompson2022escape; @duckett2022journey].  The value judgments of health economic modellers are rarely adequately specified [@duckett2022journey]. These value judgments influence the assumptions, selection of model features and standards for evidence that shape health economic model projects [@HARVARD2020112975]. For example, the process of determining CHEM *user requirements and design specifications* will involve making judgments about the competing claims of alternative software development platforms (Table \@ref(tab:proscons)). That decision will in turn determine how straightforward it is for a CHEM to be subsequently amended to reflect alternative value judgments relating to model conceptualisation and mathematical formalisation (Table \@ref(tab:timelygls)).
<!-- Moved -->
<!--  , omissions that may lead to socially unacceptable policy recommendations -->

@@

The *social benefit* of developing a CHEM may be limited if it is rarely used, if mis-used or when its acceptability and adequacy rapidly decay. Reuse of CHEMs as components of other models can potentially make model development more efficient [@Arnold2010; @garcia2021cost]. However, health economic models face challenges related to transferability across jurisdictions [@garcia2021cost] that create barriers to reuse. Without ongoing maintenance, a CHEM risks becoming less reliable with time [@garcia2021cost] and is at risk of being deployed for purposes for which it is poorly suited [@calder2018computational]. Currently, health economic models are rarely implemented computationally in a manner that facilitates routine updates [@Sampson2017], thus limiting the temporal window within which a CHEM can be validly applied. 
<!-- Moved -->
<!-- Edit --><!-- All three  -->Our proposed ethical goals are most likely to be met when there is both good<!-- have implications for both  --> professional practice by CHEM developers and <!-- Addition -->adequate <!-- Addition -->resourcing by project funders.  <!-- /Edit --> The choices CHEM developers make often need to balance ethical considerations with project resource constraints (as illustrated in Table \@ref(tab:proscons)). Modelling projects implemented by diligent and conscientious CHEM developers may still be exposed to ethical risks if there are inadequate resources to meaningfully engage important stakeholder groups, prepare code and data artefacts for independent assessment and provide ongoing model maintenance and user support. Existing incentive structures for research health economists generally do not promote facilitating peers to reuse their work and funding is rarely adequate to maintain and routinely update a model. Currently, it can take “an extraordinary amount of idealism” to commit to authoring and maintaining research software [@anzt2020environment]. For these reasons, we believe responsibility for achieving our proposed ethical goals is shared between CHEM developers and funders. Reflecting the shared nature of this responsibility, we suggest that in most cases where a modelling project fails to meet our ethical goals, it will be more appropriate to describe these shortcomings as "ethical risks" (the language used by Boden and McKendrick) than to use accusatory terms like "unethical practice."<!-- these responsibilities should apply jointly to health economic model developers and funders. -->

<!-- For example, as illustrated in Table \@ref(tab:proscons), project resource constraints may require model developers to make trade-offs -->
<!-- As it is unreasonable to place expectations of modellers that they are not resourced to fulfil,  -->
<!-- /Moved -->

<!-- # -->
# CHEM attributes that can reduce ethical risk
<!-- The responsibilities of model project teams over a CHEM lifecycle  -->
Our proposed ethical goals for each project phase are easier to state than to measure.  However, <!-- aspects of ethical modelling practice  -->achievement of these goals may be inferred from measurable attributes of CHEMs. As described in Table \@ref(tab:timelygls),  we believe that the <!-- Edit -->developers and funders<!-- /Edit --> of CHEMs that are transparent, reusable and updatable (TRU) are more likely to have achieved the ethical goals we propose. <!-- fulfilled a number of their ethical obligations.   --> 
<!-- We therefore selected these CHEM attributes to use as the basis for deriving ethical assessment criteria. -->

@@

Taking steps to make computational models *transparent* is an important means of reducing ethical risk <!-- part of ethical public health modelling practice  -->[@10.3389/fpubh.2017.00068]. Guidance on transparency in health economic modelling recommend that model code and data should be clearly documented [@Eddy2012]. Notably, the same guidelines, published over ten years ago, do not recommend sharing model code and data. However, more recent healthcare modelling guidance does recommend public dissemination of such artefacts [@Erdemir2020]. Online repository services such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection. Ensuring that calculations are correct and consistent with model specifications is an essential part of CHEM quality assurance [@techver2019]. The extensiveness of such verification checks can be reported using the concept of code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested. Tests should ideally combine both unit tests (to verify that small, isolated sections of code produce the correct output when run independently) and acceptance tests (to verify that the correct output is produced when multiple code components are run together to perform tasks that meet core user-requirements [@martin2003agile]). The nature and extent of individual model authorship contributions can become unclear when models are implemented over longer time-frames with a large and changing group of collaborators [@thompson2022escape]. This issue can be addressed by use of online repository services such as GitHub [@github2007], that provide citation tools and can transparently record all individual code contributions to a modelling project over its lifecycle.

<!-- A CHEM that is *reusable* also signals ethical modelling practice.  -->
Although making a CHEM’s code, data and documentation publicly available is increasingly considered good practice, it is insufficient to ensure that a model is *reusable*. Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39]. Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is good scientific computing practice [@Wilson_2017] and promotes selective reuse. Computational implementations that store model code and data in distinct files and locations (as opposed to embedding data such as parameter values into source code) are also easier to selectively modify. Modular implementations enable models to be constructed from multiple independently reusable and replaceable sub-models (modules) [@pan2021modular]. The programming concept inheritance [@8717448], deployed in object-oriented programming approaches, can facilitate the selective reuse and modification of model components. Granting permissions to others to use, test and adapt models and their components, can be facilitated by two broad categories of open source licenses. Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which content can be re-used. Alternatively, copyleft licenses [@copyleft2022] can be used to require that derivative works created by content users remain open-source.

@@

<!-- # -->
#	Criteria for assessing TRU attributes
We suggest six criteria (two for each attribute) against which for assessing the TRU attributes of CHEMs.

### 2024-02-15 Markdown/Manuscript/Parent_PDF/Springer.Rmd
for coauthor feedback draft

  # - firstname: Glen
  #   lastname: Wiesner
  #   #     email: glen.wiesner@heartfoundation.org.au
  #   affiliation: [4]
  # 
  # - firstname: Kate  
  #   particle: M
  #   lastname: Filia
  #   #     email: kate.filia@orygen.org.au
  #   affiliation: [2,3]
  # 
  # - firstname: Jana
  #   particle: M
  #   lastname: Menssink
  #   #     email: jana.menssink@orygen.org.au
  #   affiliation: [2,3]
  # 
  # - firstname: Petra
  #   lastname: Plencnerova
  #   #     email: pplencnerova@headspace.org.au
  #   affiliation: [5]
  # 
  # - firstname: David  
  #   lastname: Baker
  #   #     email: david.baker@orygen.org.au
  #   affiliation: [2,3]
  # 
  # - firstname: Patrick 
  #   particle: D 
  #   lastname: McGorry
  #   #     email: pat.mcgorry@orygen.org.au
  #   affiliation: [2,3]
  # 
  # - firstname: Alexandra  
  #   lastname: Parker
  #   #     email: alex.parker@vu.edu.au
  #   affiliation: [6,3]

@@

  - firstname: Caroline
    lastname: Gao
    #     email: caroline.gao@orygen.org.au
    affiliation: [2,4,1]

>>>>

  # - firstname: Glen
  #   lastname: Wiesner
  #   #     email: glen.wiesner@heartfoundation.org.au
  #   affiliation: [4]
  # 
  # - firstname: Kate  
  #   particle: M
  #   lastname: Filia
  #   #     email: kate.filia@orygen.org.au
  #   affiliation: [2,3]
  # 
  # - firstname: Jana
  #   particle: M
  #   lastname: Menssink
  #   #     email: jana.menssink@orygen.org.au
  #   affiliation: [2,3]
  # 
  # - firstname: Petra
  #   lastname: Plencnerova
  #   #     email: pplencnerova@headspace.org.au
  #   affiliation: [5]
  # 
  # - firstname: David  
  #   lastname: Baker
  #   #     email: david.baker@orygen.org.au
  #   affiliation: [2,3]
  # 
  # - firstname: Patrick 
  #   particle: D 
  #   lastname: McGorry
  #   #     email: pat.mcgorry@orygen.org.au
  #   affiliation: [2,3]
  # 
  # - firstname: Alexandra  
  #   lastname: Parker
  #   #     email: alex.parker@vu.edu.au
  #   affiliation: [6,3]
  - firstname: Caroline
    lastname: Gao
    #     email: caroline.gao@orygen.org.au
    affiliation: [2,4,1]

@@
